Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-04 related.tex
Modificacion 2 related works

\citet{Romero1995} relied on regression models using a stepwise
procedure to predict incubation and disease latency periods for the
black Sigatoka.
% 
He collected environmental data from two different farms in Costa Rica
between December 1993 and August 1995.
%
The prediction models reached coefficients of determination $R^2$ of
69\% or 78\% on the observed data for the incubation and disease
latency periods, respectively; however, the cross validation on
independent data sets failed.

More recently, \citet{Glezakos2010} used genetic algorithms (GA) and
neural networks (NN) to identify the Tobacco Rattle Virus (TRV) and
the Cucumber Green Mottle Mosaic Virus (CGMMV).
%
The method was tested against some of the most commonly used
classifiers in machine learning (Bayes classifiers, decision trees and
$k$-nearest neighbors) via cross-validation and proved their
applicability in these kind of problems.

\citet{Alves2011} used geoinformation techniques to
develop predictive models in the study of risk areas to soybean rust,
coffee leaf rust, and banana black Sigatoka, under consideration of
Brazil’s climatic characteristics and the distribution of soybean,
coffee and banana crops.
%
Temperature and rainfall data were acquired for the period from 1950
to 2000, and simulated data were generated for 2020, 2050 and 2080
using the SRES~A2 climate change scenarios.
%
Using principal components analysis, a single variable was generated
as a linear combination of 57 input variables, in order to determine
an index explaining 87\%, 88\% and 90\% of the
%
\todofn{variability}{variabilidad de qué?}  
%
of soybean, coffee and
banana crops, respectively, in municipal districts across Brazil.
%
The climatic model was used to generate the zoning of the three plant
diseases, using temperature and leaf wetness as input.
%
%Redunda con lo que sigue:
%Areas favorable for the diseases were plotted against the main coffee,
%soybean and banana growing areas in Brazil.
%
This methodology enabled the visualization of the changes in areas
favorable for epidemics under possible future scenarios of climate
change.

>>>>

\citet{Romero1995} relied on regression models using a stepwise
procedure to predict incubation and disease latency periods for the
black Sigatoka.
% 
He collected environmental data from two different farms in Costa Rica
between December 1993 and August 1995.
%
The prediction models reached coefficients of determination $R^2$ of
69\% or 78\% on the observed data for the incubation and disease
latency periods, respectively; however, the cross validation on
independent data sets failed.
%
In contrast, our proposal presents a model that can be generalizable to other farms that have data.

More recently, \citet{Glezakos2010} used genetic algorithms (GA) and
neural networks (NN) to identify the Tobacco Rattle Virus (TRV) and
the Cucumber Green Mottle Mosaic Virus (CGMMV).
%
The method was tested against some of the most commonly used
classifiers in machine learning (Bayes classifiers, decision trees and
$k$-nearest neighbors) via cross-validation and proved their
applicability in these kind of problems.
%
These authors do not prove their methods in Sigatoka disease and they do classification. Instead we do regression.

\citet{Alves2011} used geoinformation techniques to
develop predictive models in the study of risk areas to soybean rust,
coffee leaf rust, and banana black Sigatoka, under consideration of
Brazil’s climatic characteristics and the distribution of soybean,
coffee and banana crops.
%
Temperature and rainfall data were acquired for the period from 1950
to 2000, and simulated data were generated for 2020, 2050 and 2080
using the SRES~A2 climate change scenarios.
%
Using principal components analysis, a single variable was generated
as a linear combination of 57 input variables, in order to determine
an index explaining 87\%, 88\% and 90\% of the data
%
\todofn{variability}{variabilidad de qué? - Comentario: de los datos de cada uno }  
%
of soybean, coffee and
banana crops, respectively, in municipal districts across Brazil.
%
The climatic model was used to generate the zoning of the three plant
diseases, using temperature and leaf wetness as input.
%
%Redunda con lo que sigue:
%Areas favorable for the diseases were plotted against the main coffee,
%soybean and banana growing areas in Brazil.
%
This methodology enabled the visualization of the changes in areas
favorable for epidemics under possible future scenarios of climate
change.
%
How intermediate result, they characterized the monociclic process of the black Sigatoka using  nonlinear regression. Although they do not present the detailed results, it no seem that they wanted to predict the progression of the black Sigatoka one, two or more periods ahead.
